A saturation model for impaired learning with enhanced plasticity: Supplementary material

### 2013-04-15 MHCpaper/MHCsupp.tex
rearranged figures

\begin{figure}
 \begin{center}
 \begin{myenuma}
  \item\aligntop{\includegraphics[height=1.7cm]{multistate.svg}}\label{fig:multistate_model}\hspace{0.5cm}
  \item\aligntop{\includegraphics[height=1.7cm]{binary.svg}}\label{fig:binary_model}\hspace{0.5cm}
  \item\aligntop{\includegraphics[height=2.2cm]{cascade.svg}}\label{fig:cascade_model}
 \end{myenuma}
 \end{center}
  \caption[Transition probabilities for different models]{Transition probabilities for different models.
  Potentiation induces transitions indicated by solid red arrows, depression indicated by dashed blue arrows.
  States of strong/weak synaptic weight indicated by red/blue circles.
  States of strong/weak synaptic weight
  (\ref{fig:multistate_model}) In the multistate model the transition probabilities for potentiation/depression are all equal and it is parameterised by these two values.
  (\ref{fig:binary_model}) The two-state model is parameterised by the two transition probabilities.
  (\ref{fig:cascade_model}) In the cascade model, the transition probabilities decay geometrically with a parameter $x$ (see \cite{Fusi2005cascade}) and synaptic weight takes only two values.
  } \label{fig:models}
\end{figure}

@@

\newcommand{\resultsfig}[3]{\begin{figure}
 \begin{center}
 \begin{myenuma}
  \item\aligntop{\includegraphics[width=7cm]{#3_learn.eps}}\label{fig:#3_learn}
  \item\aligntop{\includegraphics[width=7cm]{#3_learnS.eps}}\label{fig:#3_learnS}
  \\ \vp\vp
  \item\label{fig:#3_eq}\begin{myenumi}
                    \item\aligntop{\includegraphics[width=7cm]{#3_eq_WT.eps}}\label{fig:#3_eq_WT}
                    \item\aligntop{\includegraphics[width=7cm]{#3_eq_KO.eps}}\label{fig:#3_eq_KO}
                  \end{myenumi}
  \\ \vp \vp
  \item\label{fig:#3_pr}\begin{myenumi}
                    \item\aligntop{\includegraphics[width=3cm]{#3_pr_WT_nopre.eps}}\label{fig:#3_pr_WT_nopre}
                    \item\aligntop{\includegraphics[width=3cm]{#3_pr_WT_pre.eps}}\label{fig:#3_pr_WT_pre}
                    \item\aligntop{\includegraphics[width=3cm]{#3_pr_KO_nopre.eps}}\label{fig:#3_pr_KO_nopre}
                    \item\aligntop{\includegraphics[width=3cm]{#3_pr_KO_pre.eps}}\label{fig:#3_pr_KO_pre}
                  \end{myenumi}
 \end{myenuma}
 \end{center}
  \caption[#1]{#1 #2.
  Other parameters can be found in \autoref{tr:#3} of \autoref{tab:params}.
  Time is measured in units of $1/r$, the mean time between plasticity events.
  (\ref{fig:#3_learn}) Learning curves for wild-type and \KO\ mutant with and without pre-training.
  (\ref{fig:#3_learnS}) Learning curves restricted to gain-increase training.
  (\ref{fig:#3_eq}) Equilibrium distributions without training or with gain-increase/decrease training for (\ref{fig:#3_eq_WT}) wild-type and (\ref{fig:#3_eq_KO}) \KO\ mutant,
  with states of weak synaptic strength to the left and strong states to the right.
  (\ref{fig:#3_pr}) Evolution of probability distributions for (\ref{fig:#3_pr_WT_nopre}\ref{fig:#3_pr_WT_pre}) wild-type and  (\ref{fig:#3_pr_KO_nopre}\ref{fig:#3_pr_KO_pre}) \KO\ mutant without (\ref{fig:#3_pr_WT_nopre},\ref{fig:#3_pr_KO_nopre}) and with (\ref{fig:#3_pr_WT_pre},\ref{fig:#3_pr_KO_pre}) pre-training,
  with states of weak synaptic strength at the top and strong states underneath. } \label{fig:#3}
\end{figure}}

\newcommand{\resultsfign}[2]{\begin{figure}
 \begin{center}
 \begin{myenuma}
  \item\aligntop{\includegraphics[width=7cm]{#2_learn.eps}}\label{fig:#2_learn}
  \item\aligntop{\includegraphics[width=7cm]{#2_learnS.eps}}\label{fig:#2_learnS}
  \\ \vp \vp
  \item\label{fig:#2_eq}\begin{myenumi}
                    \item\aligntop{\includegraphics[width=7cm]{#2_eq_WT.eps}}\label{fig:#2_eq_WT}
                    \item\aligntop{\includegraphics[width=7cm]{#2_eq_KO.eps}}\label{fig:#2_eq_KO}
                  \end{myenumi}
  \\ \vp \vp
  \item\label{fig:#2_pr}\begin{myenumi}
                    \item\aligntop{\includegraphics[width=3cm]{#2_pr_WT_nopre.eps}}\label{fig:#2_pr_WT_nopre}
                    \item\aligntop{\includegraphics[width=3cm]{#2_pr_WT_pre.eps}}\label{fig:#2_pr_WT_pre}
                    \item\aligntop{\includegraphics[width=3cm]{#2_pr_KO_nopre.eps}}\label{fig:#2_pr_KO_nopre}
                    \item\aligntop{\includegraphics[width=3cm]{#2_pr_KO_pre.eps}}\label{fig:#2_pr_KO_pre}
                  \end{myenumi}
 \end{myenuma}
 \end{center}
  \caption[#1]{#1.
  Parameters can be found in \autoref{tr:#2} of \autoref{tab:params}.
  Time is measured in units of $1/r$, the mean time between plasticity events.
  (\ref{fig:#2_learn}) Learning curves for wild-type and \KO\ mutant with and without pre-training.
  (\ref{fig:#2_learnS}) Learning curves restricted to gain-increase training.
  (\ref{fig:#2_eq}) Equilibrium distributions without training or with gain-increase/decrease training for (\ref{fig:#2_eq_WT}) wild-type and (\ref{fig:#2_eq_KO}) \KO\ mutant,
  with states of weak synaptic strength to the left and strong states to the right.
  (\ref{fig:#2_pr}) Evolution of probability distributions for (\ref{fig:#2_pr_WT_nopre}\ref{fig:#2_pr_WT_pre}) wild-type and  (\ref{fig:#2_pr_KO_nopre}\ref{fig:#2_pr_KO_pre}) \KO\ mutant without (\ref{fig:#2_pr_WT_nopre},\ref{fig:#2_pr_KO_nopre}) and with (\ref{fig:#2_pr_WT_pre},\ref{fig:#2_pr_KO_pre}) pre-training,
  with states of weak synaptic strength at the top and strong states underneath. } \label{fig:#2}
\end{figure}}

@@

\resultsfig{Simulation results for the step-multistate model with weak training}{($\Delta f=-0.1$)}{multistate_weak}

\resultsfig{Simulation results for the step-multistate model with moderate training}{($\Delta f=-0.17$)}{multistate_med}

\resultsfig{Simulation results for the step-multistate model with strong training}{($\Delta f=-0.4$)}{multistate_strong}

@@

\resultsfign{Simulation results for two-state model}{binary}

@@

\resultsfign{Simulation results for multistate model with linear weights}{multistate_lin}

@@

\resultsfig{Simulation results for the pooled resource model with light depletion}{($q\lmin/q\lmax=0.75$)}{pooled_plenty}

\resultsfig{Simulation results for the pooled resource model with heavy depletion}{($q\lmin/q\lmax=0.25$)}{pooled_scarce}

@@

\resultsfig{Simulation results for the cascade model with short pre-training}{($rt_\text{pre}=50$)}{cascade_short}

\resultsfig{Simulation results for the cascade model with long pre-training}{($rt_\text{pre}=150$)}{cascade_long}

>>>>

\begin{figure}
 \begin{center}
 \begin{myenuma}
  \item\aligntop{\includegraphics[height=1.7cm]{multistate.svg}}\label{fig:multistate_model}\hspace{0.5cm}
  \item\aligntop{\includegraphics[height=1.7cm]{binary.svg}}\label{fig:binary_model}\hspace{0.5cm}
  \item\aligntop{\includegraphics[height=2.2cm]{cascade.svg}}\label{fig:cascade_model}
 \end{myenuma}
 \end{center}
  \caption[Transition probabilities for different models]{Transition probabilities for different models.
  Potentiation induces transitions indicated by solid red arrows, depression indicated by dashed blue arrows.
  States of strong/weak synaptic weight indicated by red/blue circles.
  (\ref{fig:multistate_model}) In the multistate model the transition probabilities for potentiation/depression are all equal and it is parameterised by these two values.
  (\ref{fig:binary_model}) The two-state model is parameterised by the two transition probabilities.
  (\ref{fig:cascade_model}) In the cascade model, the transition probabilities decay geometrically with a parameter $x$ (see \cite{Fusi2005cascade}) and synaptic weight takes only two values.
  } \label{fig:models}
\end{figure}

@@

\newcommand{\arrangefig}[1]{\begin{center}
 \begin{myenuma}
  \item\aligntop{\includegraphics[width=7cm]{#1_learn.eps}}\label{fig:#1_learn}
  \item\aligntop{\includegraphics[width=7cm]{#1_learnS.eps}}\label{fig:#1_learnS}
  \\ \vp\vp
  \item\label{fig:#1_eq}\begin{myenumi}
                    \item\aligntop{\includegraphics[width=7cm]{#1_eq_WT.eps}}\label{fig:#1_eq_WT}
                    \item\aligntop{\includegraphics[width=7cm]{#1_eq_KO.eps}}\label{fig:#1_eq_KO}
                  \end{myenumi}
  \\ \vp \vp
  \item\label{fig:#1_pr}\begin{myenumi}
                    \item\aligntop{\includegraphics[width=3cm]{#1_pr_WT_nopre.eps}}\label{fig:#1_pr_WT_nopre}
                    \item\aligntop{\includegraphics[width=3cm]{#1_pr_WT_pre.eps}}\label{fig:#1_pr_WT_pre}
                    \item\aligntop{\includegraphics[width=3cm]{#1_pr_KO_nopre.eps}}\label{fig:#1_pr_KO_nopre}
                    \item\aligntop{\includegraphics[width=3cm]{#1_pr_KO_pre.eps}}\label{fig:#1_pr_KO_pre}
                  \end{myenumi}
 \end{myenuma}
 \end{center}}

\newcommand{\captiontext}[1]{ can be found in \autoref{tr:#1} of \autoref{tab:params}.
  Time is measured in units of $1/r$, the mean time between plasticity events.
  (\ref{fig:#1_learn}) Learning curves for wild-type and \KO\ mutant with and without pre-training.
  (\ref{fig:#1_learnS}) Learning curves restricted to gain-increase training.
  (\ref{fig:#1_eq}) Equilibrium distributions without training or with gain-increase/decrease training for (\ref{fig:#1_eq_WT}) wild-type and (\ref{fig:#1_eq_KO}) \KO\ mutant,
  with states of weak synaptic strength to the left and strong states to the right.
  (\ref{fig:#1_pr}) Evolution of probability distributions for (\ref{fig:#1_pr_WT_nopre}\ref{fig:#1_pr_WT_pre}) wild-type and  (\ref{fig:#1_pr_KO_nopre}\ref{fig:#1_pr_KO_pre}) \KO\ mutant without (\ref{fig:#1_pr_WT_nopre},\ref{fig:#1_pr_KO_nopre}) and with (\ref{fig:#1_pr_WT_pre},\ref{fig:#1_pr_KO_pre}) pre-training,
  with states of weak synaptic strength at the top and strong states underneath. }

\newcommand{\captionstart}[2]{Simulation results for the \textbf{#1} model with #2}
\newcommand{\captionstarts}[2]{Simulation results for the #1 model with #2}
\newcommand{\captionstartn}[1]{Simulation results for the \textbf{#1} model}
\newcommand{\captionstartsn}[1]{Simulation results for the #1 model}

\newcommand{\resultsfig}[4]{\begin{figure}
  \arrangefig{#4}
  \caption[\captionstarts{#1}{#2}]{\captionstart{#1}{#2 #3}.
  Other parameters \captiontext{#4} } \label{fig:#4}
\end{figure}}

\newcommand{\resultsfign}[2]{\begin{figure}
  \arrangefig{#2}
  \caption[\captionstartsn{#1}]{\captionstartn{#1}.
  Parameters \captiontext{#2} } \label{fig:#2}
\end{figure}}

@@

\resultsfig{step-multistate}{weak training}{($\Delta f=-0.1$)}{multistate_weak}

\resultsfig{step-multistate}{moderate training}{($\Delta f=-0.17$)}{multistate_med}

\resultsfig{step-multistate}{strong training}{($\Delta f=-0.4$)}{multistate_strong}

@@

\resultsfign{two-state model}{binary}

@@

\resultsfign{linear multistate model}{multistate_lin}

@@

\resultsfig{pooled resource}{light depletion}{($q\lmin/q\lmax=0.75$)}{pooled_plenty}

\resultsfig{pooled resource}{heavy depletion}{($q\lmin/q\lmax=0.25$)}{pooled_scarce}

@@

\resultsfig{cascade}{short pre-training}{($rt_\text{pre}=50$)}{cascade_short}

\resultsfig{cascade}{long pre-training}{($rt_\text{pre}=150$)}{cascade_long}
